Explicit Operations on Parametrised Polytopes

### 2018-01-06 dcg-draft.tex
corrected typo

  Specifically, if $z\in \partial S$ then $z\in S$ and there exists $\zeta\in\mathbb R^n$ such that $z + \epsilon \zeta \notin S$ for all $\epsilon > 0$.
  %
  From this it follows that $z = \lambda z_1 + (1-\lambda ) z_2$ for $z_1\in\partial \mathcal W(p_1)$ and $z_2\in\partial \mathcal W(p_2)$ and there exists $n\in \mathbb R^n$ such that for all $\mu \in [0,1]$ we have
  \begin{equation}\label{eq:normal_cone_cond}
    n^T \bigl( \mu \zeta_1 + (1-\mu) \zeta_2 \bigr) \leq 0 
  \end{equation}
  for all $\zeta_1$and $\zeta_2$ such that $n_1^T\zeta_1 \leq 0$ and $n_2^T\zeta_2 \leq 0$ for all $n_1\in\mathcal N_{\mathcal W}(p_1)$ and $n_2\in\mathcal N_{\mathcal W}(p_2)$. Note that these conditions are equivalent to the requirement that the normal cone to $S$ at $z$ is non-empty.
  %
  Clearly $n\in \mathcal N_{\mathcal W}(p_1)$ (since $\mu = 1$ in (\ref{eq:normal_cone_cond}) gives $n^T\zeta_1 \leq 0$) and similarly $n\in \mathcal N_{\mathcal W}(p_2)$ (since $\mu = 0$ in (\ref{eq:normal_cone_cond}) gives $n^T\zeta_2 \leq 0$), and hence $\mathcal N_{\mathcal W}(p_1,z_1) \cap \mathcal N_{\mathcal W}(p_2,z_2) \neq \emptyset$ is necessary for $z\in\partial S$.
  %
  Furthermore $n\in \mathcal N_{\mathcal W}(p_1)\cap \mathcal N_{\mathcal W}(p_2)$ is also sufficient for (\ref{eq:normal_cone_cond}) and hence also $z\in\partial S$.
  %

>>>>

  Specifically, if $z\in \partial S$ then $z\in S$ and there exists $\zeta\in\mathbb R^n$ such that $z + \epsilon \zeta \notin S$ for all $\epsilon > 0$.
  %
  From this it follows that $z = \lambda z_1 + (1-\lambda ) z_2$ for $z_1\in\partial \mathcal W(p_1)$ and $z_2\in\partial \mathcal W(p_2)$ and there exists $n\in \mathbb R^n$ such that for all $\mu \in [0,1]$ we have
  \begin{equation}\label{eq:normal_cone_cond}
    n^T \bigl( \mu \zeta_1 + (1-\mu) \zeta_2 \bigr) \leq 0 
  \end{equation}
  for all $\zeta_1$ and $\zeta_2$ such that $n_1^T\zeta_1 \leq 0$ and $n_2^T\zeta_2 \leq 0$ for all $n_1\in\mathcal N_{\mathcal W}(p_1)$ and $n_2\in\mathcal N_{\mathcal W}(p_2)$. Note that these conditions are equivalent to the requirement that the normal cone to $S$ at $z$ is non-empty.
  %
  Clearly $n\in \mathcal N_{\mathcal W}(p_1)$ (since $\mu = 1$ in (\ref{eq:normal_cone_cond}) gives $n^T\zeta_1 \leq 0$) and similarly $n\in \mathcal N_{\mathcal W}(p_2)$ (since $\mu = 0$ in (\ref{eq:normal_cone_cond}) gives $n^T\zeta_2 \leq 0$), and hence $\mathcal N_{\mathcal W}(p_1,z_1) \cap \mathcal N_{\mathcal W}(p_2,z_2) \neq \emptyset$ is necessary for $z\in\partial S$.
  %
  Furthermore $n\in \mathcal N_{\mathcal W}(p_1)\cap \mathcal N_{\mathcal W}(p_2)$ is also sufficient for (\ref{eq:normal_cone_cond}) and hence also $z\in\partial S$.
  %
